\ifthenelse{\boolean{en}}{

  \section{\textbf{Research Experiences}}
  \resumeSubHeadingListStartNoLabel
    \resumeSubheading
      {Intrusion Detection System Based on Deep Learning -- Team Leader}{IoT Innovation Lab}
      {Zhengzhou University}{Apr. 2019 -- Present}
      \resumeItemListStart
        \resumeItem{}{A model for intrusion detection based on CNN, LSTM, SVM.}
        \resumeItem{}{I am responsible for coordinating all parts of the team, including related research, model design and improvement, and related documentation. The model has reached a recognition accuracy of around 97\%.}
        \resumeItem{}{Related paper is on the way.}
      \resumeItemListEnd
      \resumeSubheading
      {Dressing-up Scene Generation Based on GANs -- Team Member}{IoT Innovation Lab}
      {Zhengzhou University}{Dec. 2018 -- Present}
      \resumeItemListStart
        \resumeItem{}{Design and build generative adversarial network models for dressing-up scene generation.}
        \resumeItem{}{I am responsible for the collection and preprocessing of data sets. I also participate in the design, construction and improving of models.}
        \resumeItem{}{It is in the final stage.}
      \resumeItemListEnd
      \resumeSubheading
      {Stock Prediction Model Based on LSTM -- Team Member}{IoT Innovation Lab}
      {Zhengzhou University}{Sep. 2017 -- Nov. 2017}
      \resumeItemListStart
        \resumeItem{}{Build a LSTM model to predict the trend of selected stocks, combined with public news to assist forecasting.}
        \resumeItem{}{I am responsible for the collection and summarization of stock-related public news, and participate in the model design of LSTM.}
        \resumeItem{}{We won the finalist award of 2017 Xiamen International Big Data Competition}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  }{
  \section{\textbf{研究经历}}
  \resumeSubHeadingListStartNoLabel
    \resumeSubheading
      {基于深度学习的入侵检测系统 -- 负责人}{物联网创新实验室}
      {郑州大学}{2019.04 -- 至今}
      \resumeItemListStart
        \resumeItem{介绍:\ }{基于CNN、LSTM、SVM等构建用于入侵检测的模型。}
        \resumeItem{职责:\ }{负责协调团队各部分工作，包括相关调研、模型设计构建与改进、相关文档的整理。模型已经达到97\%左右的识别准确率。}
        \resumeItem{成果:\ }{软件著作权一项；已经完成相关实验，论文在写。}
      \resumeItemListEnd

      \resumeSubheading
      {基于生成对抗网络的换装相关研究 -- 课题成员}{物联网创新实验室}
      {郑州大学}{2018.12 -- 至今}
      \resumeItemListStart
      \resumeItem{介绍:\ }{同研究生一起研究并设计用于换装等场景的GAN模型。}
      \resumeItem{职责:\ }{负责数据集的采集与处理和，并参与模型的设计与构建、训练并改进部分模型。}
      \resumeItem{成果:\ }{软件著作权一项；已在收尾阶段，论文在写。}
      \resumeItemListEnd

      \resumeSubheading
      {基于LSTM神经网络的选股预测模型 -- 项目成员 }{物联网创新实验室}
      {郑州大学}{2017.09 -- 2017.11}
      \resumeItemListStart
      \resumeItem{介绍:\ }{通过训练LSTM来预测选定股票的走势情况，并结合舆情分析进行辅助预测。}
      \resumeItem{职责:\ }{负责股票相关舆情信息的爬取与汇总，并参与LSTM的模型设计。}
      \resumeItem{成果:\ }{获得2017年厦门国际大数据比赛入围奖。}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
}
